%-------------------------
% Resume in Latex
% Author : Anderson Banihirwe
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://andersonbanihirwe.dev}{\Large Anderson Banihirwe}} & Email : \href{mailto:abanihi@ucar.edu}{abanihi@ucar.edu}\\
  \href{https://andersonbanihirwe.dev}{https://andersonbanihirwe.dev} &
  Github : \href{https://github.com/andersy005}{andersy005} \\
  & LinkedIn: \href{https://www.linkedin.com/in/andersy005}{andersy005} \\
\end{tabular*}



\section{\sc Summary}

I contribute to and maintain several libraries within the open source scientific Python stack,
particularly around improving scalability of Python tools in order to handle terabyte-scale
datasets on HPC and cloud platforms.

%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      { National Center for Atmospheric Research}{Boulder, CO}
      {Software Engineer}{Oct 2018 -- Present}
      \resumeItemListStart
        \resumeItem{Jupyter-forward}
          {Created \href{https://github.com/NCAR/jupyter-forward}{Jupyter-forward}, a Jupyter Lab port forwarding utility that simplifies running jupyter on remote resources.}
        \resumeItem{Xarray}
          {Served as a core developer of xarray, an open source library for working with multidimensional labeled arrays in Python.}

        \resumeItem{Intake-ESM}
          {Led the \href{https://github.com/intake/intake-esm}{intake-ESM project}, a Python data cataloguing package for working with earth system model data sets.}
        \resumeItem{Pangeo Project}
          {Contributed to the core software stack powering the \href{https://pangeo.io/}{Pangeo project}. Some of the projects I contributed to include: dask, intake.}
        \resumeItem{Data Management}
          {Led the effort to produce 100 terabytes of \href{https://registry.opendata.aws/ncar-cesm-lens/}{CESM LENS} analysis ready data in zarr format and transfer them to cloud storage.}
        \resumeItem{Outreach and Teaching}
          {Assisted with the development and delivery of \href{https://ncar.github.io/ncar-python-tutorial/posts/fall-2019-tutorial/}{in-person} and \href{https://youtu.be/a339Q5F48UQ}{online} Python education material.}


      \resumeItemListEnd

    \resumeSubheading
      {Quansight}{}
      {Intern}{June 2018 -- Sept 2018}
      \resumeItemListStart
        \resumeSubItem{xnd}
        {Developed \href{https://github.com/xnd-project/xndframes}{xndframes},a Pandas ExtensionDtype/Array backed by xnd}
        \resumeSubItem{GPU DataFrame}
         {Worked on integrating \href{https://github.com/rapidsai/cudf}{cuDF} with Apache Arrow Library.}

      \resumeItemListEnd

    \resumeSubheading
      {First Orion}{Little Rock, AR}
      {Data Scientist Intern}{Dec 2017 -- May 2018}
      \resumeItemListStart
        \resumeItem{Machine Learning}{Designed and built scoring, predictive models with Scikit-learn using First Orion' s proprietary telecommunication data.}
        \resumeItem{Data Processing}
          {Identified patterns and characteristics within First Orion's data warehouses using Dask, Apache Spark, Pandas.}

      \resumeItemListEnd

    \resumeSubheading
      { National Center for Atmospheric Research}{Boulder, CO}
      {Research Intern}{May 2017 -- Aug 2017}
      \resumeItemListStart
        \resumeItem{Installation}
          {Installed Apache Spark v2.2 on both Cheyenne and Yellowstone Supercomputers.}
        \resumeItem{Schedulers}
          {Cleaned/fixed Spark launch bash scripts that work with the LSF/PBS schedulers.}

        \resumeItem{spark-xarray}
          {Wrote \href{https://ncar.github.io/PySpark4Climate/} {spark-xarray }, a Python package that integrates PySpark and xarray for Climate Data Analysis.}


      \resumeItemListEnd


  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {University of Arkansas at Little Rock}{Little Rock, AR}
    {Bachelor of Science in (Computer) Systems Engineering}{Aug 2014 -- May 2018}
\resumeSubHeadingListEnd




%----------------SELECTED PRESENTATIONS---------
\section{selected publications, and talks}
  \resumeSubHeadingListStart

   \resumeSubItem{\href{https://www.authorea.com/doi/full/10.22541/au.160443768.88917719}{Cloud-Native Repositories for Big Scientific Data}}{Authored with Ryan Abernathey, Tom Augspurger, et al. Computing in Science and Engineering. Nov 2020.}

    \resumeSubItem{\href{https://talks.andersonbanihirwe.dev/climpred-cdpw-2020.html}{Analyzing Initialized Climate Prediction System Datasets with climpred}}{Invited talk about climpred, a Python package for weather and climate forecasts. NOAA's 45th Climate Diagnostics and Prediction Workshop. Oct 2020.}

    \resumeSubItem{\href{https://doi.org/10.31223/X5ZW2T}{Pangeo Benchmarking Analysis: Object Storage vs. POSIX File System}}{Authored with Haiying Xu, Kevin Paul. Fifth International Parallel Data Systems Workshop @ SC 20. Nov 2020. }
    \resumeSubItem{\href{https://talks.andersonbanihirwe.dev/zarr-cloud-native-geospatial-2020.html}{Zarr: chunked, compressed, multidimensional arrays}}{Invited talk about Zarr, an open source data format for the storage of chunked, compressed, multidimensional arrays. Cloud Native Geospatial Outreach Day 2020.}



  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
